Basic Parameter estimation of Binary Neutron Star Systems by the Advanced LIGO/Virgo Network

### 2013-09-04 doc/paper.tex
quick git test
ALMOST fixed everything

Two previous studies have considered the increase in sensitivity from the addition of the LIGO India site. \carl{[INCOMPLETE]}

@@

@@

\begin{figure}[ht!]
  \centering \includegraphics[trim=0cm 0cm 0cm 0cm,
    clip=true,scale=0.52]{noisePDF.pdf}
 \caption{The effects of a non-zero noise realization on the recovered
   PDF for five different Gaussian realizations of the Advanced LIGO
   noise curve.  Each PDF represents the recovery of the same
   $1M_{\odot}/2.5M_{\odot}$ signal in a different noise curve, picked
   at random from the Gaussian colored noise defined by the Advanced
   LIGO power spectral density, while the gray-shaded curve is the
   zero-noise PDF.  Notice how each curve is a Gaussian PDF with roughly similar shape,
   but different mean, to the zero-noise PDF.  This
   only holds true for glitch-free data, which is an unrealistic
   idealization when compared to real data.}
 \label{noisePDFs}
\end{figure}

>>>>

Two previous studies have considered the increase in sensitivity from the addition of the 
LIGO India site. \cite{Veitch2012} and \cite{Nissanke2013} studied the decrease in
sky-location uncertainties obtained by the inclusion of the LIGO India site
into the advanced detector network.  Both studies employed an MCMC sampling technique 
(Veitch et al.\ via \texttt{LALInference}, Nissanke et al. via a modified version of CosmoMC),
to determine the average parameter estimation uncertainties for a realistic distribution
of sources in co-moving volume.  As the current study is interested in the uncertainties
of optimal sources at $\text{SNR}_{network}=20$, ignoring the effects of less viable 
detection candidates, it is instructive to compare the $95\%$ credible intervals
between the three studies.  The cumulative distributions of sky-area uncertainties
for both network configurations in each study are plotted in Fig. \ref{compSky}.

@@

\begin{figure}[ht!]
  \centering \includegraphics[angle=0,scale=0.58, trim=0.5cm 1cm 0cm 0cm]{comparitiveSkyAreas.pdf}

 \caption{The cumulative fraction of sources found within $deg^2$ at the 95\% credible
 interval.  This plot contains results from three separate studies: the current study, in
 which optimal detection candidates are considered ($SNR_{network}=20$), 
 \cite{Veitch2012}, which employs several \texttt{LALInference} samplers (including the
 MCMC sampler used here) on an source population evenly distributed in co-moving 
 volume, and \cite{Nissanke2013}, which employs a separate MCMC code on a
 realistic source population.  The optimal detection candidates are constrained
 to substantially smaller solid angles on the sky, as is expected for such ``gold-plated''
 events.}
 \label{compSky}
\end{figure}

@@

\begin{figure}[ht!]
  \centering \includegraphics[trim=0cm 0cm 0cm 0cm,
    clip=true,scale=0.52]{noisePDF.pdf}
 \caption{The effects of a non-zero noise realization on the recovered
   PDF for five different Gaussian realizations of the Advanced LIGO
   noise curve.  Each blue-dashed PDF represents the recovery of the same
   $1M_{\odot}/2.5M_{\odot}$ signal in a different noise curve, picked
   at random from the Gaussian colored noise defined by the Advanced
   LIGO power spectral density, while the gray-shaded curve is the
   zero-noise PDF.  Notice how each curve is a Gaussian PDF with roughly similar shape,
   but different mean, to the zero-noise PDF.  This
   only holds true for glitch-free data, which is an unrealistic
   idealization when compared to real data.}
 \label{noisePDFs}
\end{figure}
